\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-09-01 Paper/Paper.tex
Complete refining abnormity ROC
Refine D1 confusion matrix
Refine Abnormities confusion matrices
Refine D2 confusion matrix
Refine D2 tSNE
adjust layout.

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.8\linewidth]{Figs/criteria.pdf}
		\caption{Abnormity-to-disease Deduction Criteria}
		\vspace{0.3cm}
		\label{fig:criteria}
	\end{figure}

@@

	In Stage D2, we determine the final disease probability vector. Similarly, we use a fused vector from the outputs of submodels in Stage D1, and have the vector go through a FC layer with softmax operation. The result presents potential diseases that can be referenced by ophthalmologists.

@@

	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{OCT abnormities}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV    &2984&-  &- &- &2984\\
					CSC    &-   &102&32&- &134 \\
					DME    &2500&-  &- &- &2500\\
					Drusen &2500&-  &- &- &2500\\
					ERM    &-   &-  &- &16&16  \\
					IF     &1097&-  &- &- &1097\\
					MH     &-   &99 &31&- &130 \\
					Mactel &-   &-  &29&- &29  \\
					Healthy&5000&-  &- &- &5000\\
					RP     &-   &102&31&- &133 \\
					ST     &-   &-  &23&- &23  \\
					SF     &1083&-  &- &- &1083\\
					\bottomrule
				\end{longtable}

@@

	For OCT abnormities with less than 1000 images, we use Cycle-GAN \autocite{Zhu_Park_Isola_Efros_2020} to generate new images. We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images. We go through all generated images and adopt those that clearly display only the abnormity of interest. The adoption rates are shown in Table~\ref{tb:cycleGAN_number}. Fundus images are not generated using Cycle-GAN because generated fundus images are too blurry; in addition, fundus abnormities are usually less salient than OCT ones and cannot be properly learned by Cycle-GAN, given that we only have a small number of fundus images.

@@

	We split the images, including generated images, into training and test datasets, and implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images. The rotation is only applied to images in the train dataset. Eventually, we get 5000 train images and 500 test images for each OCT abnormity, and 3000 train images and 300 test images for each fundus abnormity.

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
	\end{figure}
	\begin{figure}[htbp]
		\centering
		\vspace{-1cm}
		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
		\caption{Abnormity training}
		\vspace{0.3cm}
		\label{fig:A_train}
	\end{figure}

@@

@@

@@

			\begin{table}[htbp]
				\centering
				\fontsize{9}{12}\selectfont{
				\caption{OCT Test}
				\label{tb:OCT_test}
				\pgfplotstabletypeset[
				multicolumn names,
				col sep=comma,
				columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
				columns/Abnormity/.style={string type, column name=Abnormities},
				columns/Precision/.style={string type, column name=Precision},
				columns/Sensitivity/.style={string type, column name=Sensitivity},
				columns/Specificity/.style={string type, column name=Specificity},
				columns/FOne/.style={string type, column name={F1 Score}},
				columns/AUC/.style={string type, column name=AUC},
				every head row/.style={before row=\toprule, after row=\midrule},
				every last row/.style={ after row=\bottomrule}
				]{Tables/abnormity_o_test.csv}}
			\end{table}

			\begin{table}[htbp]
				\centering
				\fontsize{9}{12}\selectfont{
				\caption{Fundus Test}
				\label{tb:Fundus_test}
				\pgfplotstabletypeset[
				multicolumn names,
				col sep=comma,
				columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
				columns/Abnormity/.style={string type, column name=Abnormities},
				columns/Precision/.style={string type, column name=Precision},
				columns/Sensitivity/.style={string type, column name=Sensitivity},
				columns/Specificity/.style={string type, column name=Specificity},
				columns/FOne/.style={string type, column name={F1 Score}},
				columns/AUC/.style={string type, column name=AUC},
				every head row/.style={before row=\toprule, after row=\midrule},
				every last row/.style={after row=\bottomrule}
				]{Tables/abnormity_f_test.csv}}
			\end{table}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.8\linewidth]{Figs/abnormity_confusion_matrix.pdf}
		\caption{A Conf Mat}
		\vspace{0.3cm}
		\label{fig:A_conf_mat}
	\end{figure}

@@

	\begin{table}[htbp]
		\centering
		\fontsize{9}{12}\selectfont{
		\caption{Diagnosis Test}
		\label{tb:diagnosis_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={ after row=\bottomrule}
		]{Tables/diagnosis2.csv}}
	\end{table}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/diagnosis2_confusion_matrix.pdf}
		\caption{D2 Conf Mat}
		\vspace{0.3cm}
		\label{fig:D2_conf_mat}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/diagnosis2_tSNE.pdf}
		\caption{D2 tSNE}
		\vspace{0.3cm}
		\label{fig:D2_tSNE}
	\end{figure}

	\section{Discussion}

>>>>

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.7\linewidth]{Figs/criteria.pdf}
		\caption{Abnormity-to-disease Deduction Criteria}
		\vspace{0.3cm}
		\label{fig:criteria}
	\end{figure}

@@

	\begin{multicols}{2}	
	In Stage D2, we determine the final disease probability vector. Similarly, we use a fused vector from the outputs of submodels in Stage D1, and have the vector go through a FC layer with softmax operation. The result presents potential diseases that can be referenced by ophthalmologists.

@@

	For OCT abnormities with less than 1000 images, we use Cycle-GAN \autocite{Zhu_Park_Isola_Efros_2020} to generate new images. We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images. We go through all generated images and adopt those that clearly display only the abnormity of interest. The adoption rates are shown in Table~\ref{tb:cycleGAN_number}. Fundus images are not generated using Cycle-GAN because generated fundus images are too blurry; in addition, fundus abnormities are usually less salient than OCT ones and cannot be properly learned by Cycle-GAN, given that we only have a small number of fundus images.
	\end{multicols}

	\vspace{-0.5cm}
	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{OCT abnormities}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV    &2984&-  &- &- &2984\\
					CSC    &-   &102&32&- &134 \\
					DME    &2500&-  &- &- &2500\\
					Drusen &2500&-  &- &- &2500\\
					ERM    &-   &-  &- &16&16  \\
					IF     &1097&-  &- &- &1097\\
					MH     &-   &99 &31&- &130 \\
					Mactel &-   &-  &29&- &29  \\
					Healthy&5000&-  &- &- &5000\\
					RP     &-   &102&31&- &133 \\
					ST     &-   &-  &23&- &23  \\
					SF     &1083&-  &- &- &1083\\
					\bottomrule
				\end{longtable}

@@

@@

	\begin{multicols}{2}
	We split the images, including generated images, into training and test datasets, and implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images. The rotation is only applied to images in the train dataset. Eventually, we get 5000 train images and 500 test images for each OCT abnormity, and 3000 train images and 300 test images for each fundus abnormity.

@@

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
		\caption{Abnormity training}
		\label{fig:A_train}
	\end{figure}

@@

	\begin{table}[htbp]
		\centering
		\fontsize{9}{12}\selectfont{
		\caption{OCT Test}
		\label{tb:OCT_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={ after row=\bottomrule}
		]{Tables/abnormity_o_test.csv}}
	\end{table}
	\begin{table}[H]
		\centering
		\fontsize{9}{12}\selectfont{
		\caption{Fundus Test}
		\label{tb:Fundus_test}
		\pgfplotstabletypeset[
		multicolumn names,
		col sep=comma,
		columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
		columns/Abnormity/.style={string type, column name=Abnormities},
		columns/Precision/.style={string type, column name=Precision},
		columns/Sensitivity/.style={string type, column name=Sensitivity},
		columns/Specificity/.style={string type, column name=Specificity},
		columns/FOne/.style={string type, column name={F1 Score}},
		columns/AUC/.style={string type, column name=AUC},
		every head row/.style={before row=\toprule, after row=\midrule},
		every last row/.style={after row=\bottomrule}
		]{Tables/abnormity_f_test.csv}}
	\end{table}

	\pagebreak

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_confusion_matrix.pdf}
		\caption{A Conf Mat}
		\vspace{0.3cm}
		\label{fig:A_conf_mat}
	\end{figure}

		\vspace{1.5cm}

@@

@@

@@

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.7\linewidth]{Figs/diagnosis2_confusion_matrix.pdf}
		\vspace{-0.8cm}
		\caption{D2 Conf Mat}
		\label{fig:D2_conf_mat}
	\end{figure}

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.65\linewidth]{Figs/diagnosis2_tSNE.pdf}
		\vspace{-0.3cm}
		\caption{D2 tSNE}
		\label{fig:D2_tSNE}
	\end{figure}

		\begin{table}[H]
		\centering
		\fontsize{9}{12}\selectfont{
			\caption{Diagnosis Test}
			\label{tb:diagnosis_test}
			\pgfplotstabletypeset[
			multicolumn names,
			col sep=comma,
			columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
			columns/Abnormity/.style={string type, column name=Abnormities},
			columns/Precision/.style={string type, column name=Precision},
			columns/Sensitivity/.style={string type, column name=Sensitivity},
			columns/Specificity/.style={string type, column name=Specificity},
			columns/FOne/.style={string type, column name={F1 Score}},
			columns/AUC/.style={string type, column name=AUC},
			every head row/.style={before row=\toprule, after row=\midrule},
			every last row/.style={ after row=\bottomrule}
			]{Tables/diagnosis2.csv}}
	\end{table}

	\vspace{1cm}

	\begin{multicols}{2}
	\section{Discussion}
